%!TEX root=cs111F2014-lab09.tex
% mainfile: cs111F2014-lab09.tex

\input{111pre}
\begin{document}
\MYTITLE{Lab 9 for Sections 03 and 04 \\ 6 November 2014\\
Due Thursday, 13 November by 2:30pm }

\vspace{-0.2in}
\subsection*{Objectives}
\vspace{-0.05in}

To further enhance your experience with designing, implementing, and enhancing Java methods, including the completion of
tasks such as creating and calling methods that use complex conditional logic and iteration constructs.  Additionally,
to practice using Java methods that read input from a text file with the {\tt java.util.Scanner}.

\vspace{-0.15in}
\subsection*{General Guidelines for Labs}
\vspace{-0.05in}

\begin{itemize}
\item
{\bf Work on the Alden Hall computers.} If you want to work on a different
machine, be sure to transfer your programs to the Alden
machines and re-run them before submitting.
\item
  {\bf Update your repository often!} You should {\tt add}, {\tt commit}, 
  and {\tt push} your updated files each time you work on them.  I will not grade 
your programs until the due date has passed.
\item
{\bf Review the Honor Code policy.} You
may discuss programs with others, but programs that are nearly identical
to others will be taken as evidence of violating the Honor Code.
\end{itemize}

\vspace{-0.15in}
\subsection*{Reading Assignment}
\vspace{-0.05in}

To continue to learn more about {\tt if/else if/else} statements and boolean expressions, please again review Sections
5.1--5.3. Since this assignment will also require you to continue to use Java classes and methods, you should once again
review Sections 4.1--4.5.  To best prepare for the new content in this laboratory assignment, you should also study
Sections 5.1--5.6, paying particularly close attention to the material about {\tt while} loops, {\tt break} and {\tt
  continue} statements, text file input, iterators, and the {\tt java.util.ArrayList} class. Students who are not
familiar with text-based todo list management tools are encouraged to review, as an example, \url{http://todotxt.com/}.

\vspace{-0.1in}
\subsection*{Create a New Directory and Starting the Project}
\vspace{-0.05in}

After changing into the {\tt cs111F2014-share/} directory, which contains our course's version control repository, you
should type the command ``{\tt git pull}'' to download the source code for this laboratory assignment.  In your own {\tt
  cs111F2014-<your user name>} repository inside the {\tt labs/} directory, create a directory called {\tt lab9}. Using
the method described in a previous laboratory assignment, please copy the source code from the share repository to your
own repository. Now, change into the {\tt labs/lab9/} directory, in your own Git repository, and use {\tt gvim} to study
the source code of the provided files. What methods do these classes provide? How do they work? 

The Java classes that you have downloaded provide the preliminary features for a complete todo list manager program. As
part of this assignment, you will document all of the provided source code and then add new methods that furnish new
features.  Then, you will run this program multiple times to demonstrate the correctness of the finished system. To
start this assignment, it is a good idea to draw diagrams like the ones in Figures 4.4 and 4.7 to understand both the
classes involved in the program and the flow of control between method invocations. Next, to understand the structure of
the {\tt TodoList} class, you may want to use the Lightweight Java Visualizer (LJV), as explained in a previous
assignment, to create an diagram of its structure in the computer's memory.

\vspace{-0.1in}
\subsection*{Understanding the Todo List Manager System}
\vspace{-0.05in}

The current implementation of the todo list manager reads from a file called ``{\tt todo.txt}'', an example of which is
included below this paragraph. An individual line in the ``{\tt todo.txt}'' file always adheres to the format
``Priority, Category, Task'' where ``A'' is the most important priority (with ``B'' being the next level, and so on),
``Understand'' being an example of a category, and ``Use the LJV to see the TodoList'' is a task.

\vspace{-0.05in}
\begin{verbatim}
A, Understand, Draw a diagram(s) to explain classes
A, Understand, Use the LJV to see TodoList
B, Explain, Add comments to all of the Todo classes 
\end{verbatim}
\vspace{-0.05in}

\vspace{-0.1in}
\subsection*{Implementing New Features}
\vspace{-0.05in}

The final version of your todo list manager should provide features to read the todo list, search for specific tasks
according to both priority and category, mark a task as done, and list all of the current tasks.  Currently, the system
does include the source code for implement the priority-search and category-search features.

\vspace{-0.05in}
\begin{verbatim}
Welcome to the Todo List Manager!
What operation would you like to perform?
Available options: read, priority-search, category-search, done, list, quit
read
list
0, A,  Understand,  Draw a diagram(s) to explain classes, done? false
1, A,  Understand,  Use the LJV to see TodoList, done? false
2, B,  Explain,  Add comments to all of the Todo classes , done? false
done
What is the id of the task?
1
list
0, A,  Understand,  Draw a diagram(s) to explain classes, done? false
1, A,  Understand,  Use the LJV to see TodoList, done? true
2, B,  Explain,  Add comments to all of the Todo classes , done? false
quit
\end{verbatim}
\vspace{-0.05in}

\vspace{-0.05in}
\vspace{-0.2in}
\subsection*{Required Deliverables}
\vspace{-0.05in}

For this assignment you are invited to submit electronic versions of the following deliverables through both the Bitbucket
repository and in a signed and printed format.

\vspace{-0.05in}
\begin{enumerate}
    \setlength{\itemsep}{0pt}
  \item Completed and properly formatted {\tt SudokuChecker.java} and {\tt SudokuCheckerMain.java} files.

  \item An output file containing outputs obtained from running {\tt SudokuCheckerMain} five times.
        
\end{enumerate}
\vspace{-0.05in}

\noindent As you complete this step, you should make sure that you created a {\tt lab9/} directory within your Git
repository.  Then, you can save all of the required deliverables in the {\tt lab9/} directory---please see the course
instructor or a teaching assistant if you are not able to create your directory properly. 

\noindent In addition to turning in signed and printed copies of your code and output, share your source code and the output
file with me through your Git repository by correctly using ``{\tt git add}'', ``{\tt git commit}'', and ``{\tt git
  push}'' commands. When you are done, please ensure that the Bitbucket Web site has a {\tt lab9/} directory in your
repository with the two Java files in the list of deliverables and the {\tt output} file. Please see the instructor
if you have questions about assignment submission.

% In addition to turning in signed and printed copies of your code and output, please share your program and the output
% file with me through your Git repository by correctly using the ``{\tt git add}'', ``{\tt git commit}'', and ``{\tt git
% push}'' commands. When you are done, please ensure that the Bitbucket Web site has a {\tt lab8/} directory in your
% repository with the four files called {\tt Lab8.java}, {\tt Lab8Main.java}, and {\tt output}. You
% should see the instructor or a teaching assistant if you have questions about submitting this assignment.

In adherence to the Honor Code, students should complete this assignment on an individual basis. While it is appropriate
for students in this class to have high-level conversations about the assignment, it is necessary to distinguish
carefully between the student who discusses the principles underlying a problem with others and the student who produces
assignments that are identical to, or merely variations on, someone else's work.  Deliverables that are nearly identical
to the work of others will be taken as evidence of violating the \mbox{Honor Code}.  

\end{document}

\begin{verbatim}
Sample Run

Welcome to the Sudoku Checker v1.0!

This program checks simple, small, 4x4 Sudoku grids for correctness. Each column, row and 2x2 region contains the numbers 1 through 4 only once.

To check your Sudoku, enter your board one row at a time, with each digit separated by a space.  Hit ENTER at the end of a row.

Enter Row 1: 1 2 3 4
Enter Row 2: 3 4 2 1
Enter Row 3: 1 2 3 4
Enter Row 4: 4 3 2 1

Thank you.  Now checking ...

REG-1:GOOD
REG-2:GOOD
REG-3:GOOD
REG-4:GOOD
ROW-1:GOOD
ROW-2:GOOD
ROW-3:GOOD
ROW-4:GOOD
COL-1:BAD
COL-2:BAD
COL-3:GOOD
COL-4:GOOD

SUDO:INVALID



Sample Run
Welcome to the Sudoku Checker v1.0!

This program checks simple, small, 4x4 Sudoku grids for correctness. Each column, row and 2x2 region contains the numbers 1 through 4 only once.

To check your Sudoku, enter your board one row at a time, with each digit separated by a space.  Hit ENTER at the end of a row.

Enter Row 1: 3 2 4 1
Enter Row 2: 4 1 3 2
Enter Row 3: 1 4 2 3
Enter Row 4: 2 3 1 4

REG-1:GOOD
REG-2:GOOD
REG-3:GOOD
REG-4:GOOD
ROW-1:GOOD
ROW-2:GOOD
ROW-3:GOOD
ROW-4:GOOD
COL-1:GOOD
COL-2:GOOD
COL-3:GOOD
COL-4:GOOD

SUDO:VALID

\end{verbatim}



\end{document}
