%!TEX root=cs111F2014-lab06.tex
% mainfile: cs111F2014-lab06.tex

\input{111pre}
\begin{document}
\MYTITLE{Lab 2 for Sections 03 and 04\\9 October 2014\\Due Thursday, 16 October by 2:30 pm}
%\MYHEADERS{Lab 2}{Due 12 Sep, 2pm}

\subsection*{Objectives}

In this laboratory assignment, you will learn more about using the {\tt java.lang.Math} class to perform numerical
calculations, further explore the creation of formatted output, learn how to use enumerated types, and practice calling
methods in another Java class.  Additionally, since real-world software developers often have to debug source code
created by other developers and add features to existing code, you will participate in a ``bug hunt'' and add new
source code to an existing system. Ultimately, you will create a working program that comprised of two Java classes.

\vspace*{-.1in}
\subsection*{General Guidelines for Labs}

\begin{itemize}
\item
{\bf Work on the Alden Hall computers.} If you want to work on a different
machine, be sure to transfer your programs to the Alden
machines and re-run them before submitting.
\item
{\bf Update your repository often!} You should add, commit, 
and push your updated files each time you work on them.  I will not grade 
your programs until the due date has passed.
\item
{\bf Review the Honor Code policy.} You
may discuss programs with others, but programs that are nearly identical
to others will be taken as evidence of violating the Honor Code.
\end{itemize}

\vspace*{-.2in}
\subsection*{Reading Assignment}

After reviewing all of the assignment sheets for the past laboratory and practical sessions and the course slides and notes,
you should read Sections 3.5 through 3.8 of your textbook.

\vspace*{-.1in}
\subsection*{Participating in a ``Bug Hunt''}

After changing into the {\tt cs111F2014-share/} directory, which contains our course's version control repository, you
should type the command ``{\tt git pull}'' to download the source code for this laboratory assignment. Now, change into
the {\tt labs/lab6} directory and use {\tt gvim} to study the source code of the {\tt CommandLineGeometer.java} and {\tt
  GeometricCalculator.java} files. What methods do these classes provide? How do they work? Does any of this code look
incorrect? Why?

After carefully reviewing the source code and PP 3.6, 3.7, and 3.9 on page 158 of your textbook and then compiling and
running the {\tt CommandLineGeometer} class, you should notice that there are several defects in this program. As
such, you will need to take part in a ``bug hunt'' to find and fix all of the problems! First, you should find the
method responsible for calculating the volume of a sphere. Using the equation in PP 3.6 as a reference point, what is
the defect in this method?

The {\tt GeometricCalculator} also provides a method to calculate a triangle's area.  Once again, there is a
mistake in this method.  Can you find and fix it? How did you know that this was the bug? If you investigate the source
code of the method for calculating the volume of a cylinder, you will notice that there is another defect lurking in the
source code. Wait! If you carefully study the way in which the {\tt CommandLineGeometer} calls the method
provided by the {\tt GeometricCalculator} and then displays the resulting output, you will realize that there is another
bug in this program. Make sure you have found all of the problems before continuing with this assignment.

\vspace*{-.1in}
\subsection*{Extending the Geometry Calculator}

\begin{sloppypar}
After reviewing the aforementioned programming projects on page 158 of your textbook, you will also notice that the {\tt
  GeometricCalculator.java} does not contain methods for calculating the surface area of a sphere or a cylinder.  While
avoiding the types of mistakes that you corrected in the previous phase of this assignments, please add in new methods
to perform these calculations. In addition, you will need to add appropriate input and output statements and method
calls to the {\tt CommandLineGeometer} to ensure that the entire program works correctly. For instance, you will need to
implement a new method called {\tt calculateSphereSurfaceArea} to the {\tt GeometricCalculator.java} file and then add
input and output code to the {\tt CommandLineGeometer.java} file. Whenever possible, try to follow the correct
pattern established in the provided source code. Please see a course instructor if you have questions!
\end{sloppypar}

As you continue to critically review the source code of the {\tt CommandLineGeometer}, you will notice that it does not
always consistently produce output for the user.  For example, even though it displays the user-input radius before
calling {\tt calculateSphereVolume}, it does not appropriately display the sides of the triangle for the {\tt
  computeTriangleArea} method---can you please add in this feature? Moreover, none of the output of the {\tt double}
variables in the {\tt CommandLineGeometer} is formatted in a consistent fashion. To solve this problem, you should use
one of the techniques described in Section 3.6 of your textbook to format the output of all decimals to contain four
decimal points. For instance, you may consider creating an instance of the {\tt DecimalFormat} class.

\subsection*{Required Deliverables}

This assignment invites you to submit electronic versions of the following deliverables through the Bitbucket repository
that you created during the first practical assignment.  As you complete this step, you should make sure that you
created a {\tt lab2/} directory within the Git repository.  Then, you can save all of the required deliverables in the
{\tt lab2/} directory---please see the course instructor or a teaching assistant if you are not able to create your
directory properly.  Additionally, students should submit signed and printed versions of all the required deliverables.

\begin{enumerate}

	\item A completed, properly commented and formatted {\tt Lab2.java} program.

        \item The output from running {\tt Lab2} in the terminal window. You may use {\tt gvim} to save your output as
          follows: using the mouse, select everything from the ``{\tt java Lab2}'' command to the end of your output.
          Right-click on the selected text and copy it.  Type ``{\tt gvim output}''---note that this {\em not} a Java
          program!---and use the ``Edit/Paste'' menu item to paste your program's output into the file.  Now, use ``{\tt
          :w}'' or the ``File/Save'' menu item to save this file.

\end{enumerate}

Share your program and the output file with me through your Git repository by correctly using ``{\tt git add}'', ``{\tt
git commit}'', and ``{\tt git push}'' commands. When you are done, please ensure that the Bitbucket Web site has
a {\tt lab2/} directory in your repository with the two files called {\tt Lab2.java} and {\tt output}. You should see 
the instructor if you have questions about assignment submission.

In adherence to the Honor Code, students should complete this assignment on an individual basis. While it is appropriate
for students in this class to have high-level conversations about the assignment, it is necessary to distinguish
carefully between the student who discusses the principles underlying a problem with others and the student who produces
assignments that are identical to, or merely variations on, someone else's work.  With the exception of the source code
that was provided in the Git repository, deliverables that are nearly identical to the work of others will be taken as
evidence of violating the \mbox{Honor Code}.  

\end{document}
